### 2014-02-27 paper/concrete.tex
checkpoint.

@@

This isn't trivial, as it is not sound to add arbitrary additional
conditions on evaluation rules.  To see this, consider a contrived
concrete system where we add a premise to a reduction rule that
stops a task based on secret information.  Such a system will
not satisfy non-interference, as it allows other tasks on the
same level to observe the termination of that task and thus the
secret information which was used to decide if the task terminates
or not.
\Red{This last part is written poorly.  Let's do it better, or remove it.}

@@

\Red{Say what do we do here.}

>>>>

\Red{In this section I only talk about TSNI.  Once we finish the previous
  section to both talk about TSNI and TINI, we should do the same here.}

@@

%This isn't trivial, as it is not sound to add arbitrary additional
%conditions on evaluation rules.  To see this, consider a contrived
%concrete system where we add a premise to a reduction rule that
%stops a task based on secret information.  Such a system will
%not satisfy non-interference, as it allows other tasks on the
%same level to observe the termination of that task and thus the
%secret information which was used to decide if the task terminates
%or not.

@@

We now have a concrete semantics, which both uses a different
representation for some of the constructs in language (a single
heap rather than a heap per task in our running example), as well
as restricting some of the operational rules to disallow
undesirable transitions.  To show that the concrete semantics
still satisfy TSNI, we use two techniques.  First, we give a
condition on what kind of restrictions can be allowed on the
operational rules.  Secondly, we define the notation of an
isomorphism between IFC languages and show that it preserves
non-interference.

Intuitively, there are two scenarios in which non-interference
can be violated when restricting the transition relation:
\begin{itemize}
  \item Adding an additional premise to one of the rules that inspects
  information which is above the security label of the thread currently
  executing.
  \item
\end{itemize}
